Verifying Demonstrations

### 2017-10-03 SystemModel.tex
Fixes slides for system model
Adds WIP on linkability and designated protest (WIP #27)

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause.

@@

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause, 
its time and its location.
More specifically, we will use the following definition.

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}

>>>>

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause.%
\label{CauseIsTheCommonDenominator}

@@

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause 
(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
More specifically, we will use the following definition.

@@

We can now define the participation count as follows.
\begin{frame}
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}

\mode<presentation>{%
  \begin{example}
    \begin{itemize}
      \item The strength function can regulate trust in witnesses.
      \item E.g.\ return the number of witnesses.
      \item \(\theta\) would control threshold of number of witnesses.
    \end{itemize}
  \end{example}
}
\end{frame}

### 2017-10-03 protocol.tex
Adds WIP on linkability and designated protest (WIP #27)

>>>>

\subsubsection{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one individual 
can provide two participation proofs and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event.
E.g.\ there might be a counter protest at the same time and place, these would 
have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
The idea is to construct a unique identifier for a protest.

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest.
(As shown in \cref{ProofFig}.)

\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another system that makes it non-interactive, see issue 
  \#27.
}.
